quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-09 paper-quollr.Rmd
Added script paths

```{r}
#| label: read-limb-nldr
# Read a variety of different NLDR representations of limb
# and plot them on same aspect ratio

@@

```{r}
#| label: combine-error-data-muscles

@@

```{r data-limb}
data_limb <- read_rds("data/limb_muscles/facs_limb_muscles_pcs_10.rds")

>>>>

<!--scripts/FACs/02_gen_embeddings.R-->
```{r}
#| label: read-limb-nldr
# Read a variety of different NLDR representations of limb
# and plot them on same aspect ratio

@@

<!--scripts/FACs/03_gen_mse_for_diff_methods.R-->
```{r}
#| label: combine-error-data-muscles

@@

<!--scripts/FACs/01_data_preprocessing.R-->
```{r data-limb}
data_limb <- read_rds("data/limb_muscles/facs_limb_muscles_pcs_10.rds")
